---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TVTmatching

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/jaromilfrossard/TVTmatching/branch/master/graph/badge.svg)](https://app.codecov.io/gh/jaromilfrossard/TVTmatching?branch=master)
<!-- badges: end -->

The `TVTmatching` is an implement of a matching algorithm with time-varying treatment. Each case is assign to one or several controls such that their time "at risk of the treatment" matches.

## Installation

You can install the development version of `TVTmatching` like so:

``` r
remotes::intall_github("jaromilfrossard/TVTmatching")
```

## Example

You can explore the control candidates for each case using:

```{r summary}
library(TVTmatching)
data("tvtdata")
tvt_sum <- tvt_summary_cases(tvtdata,
                             date_statrisk = stos,
                             date_treatna = treatna,
                             date_eos = eos,
                             state_eos = eos01, 
                             by = fct)
tvt_sum
```

You can match using dates:

```{r date}
set.seed(42)
tvt_match<- tvt_matching_date(data = tvtdata,
                              date_statrisk = stos,
                              date_treatna = treatna,
                              date_eos = eos,
                              state_eos = eos01)
tvt_match
```

If you have data in time you can use:

```{r num}
set.seed(42)
tvtdata_num <- tvt_date2numeric(data = tvtdata,
                                date_statrisk = stos,
                                date_treatna = treatna,
                                date_eos = eos,
                                state_eos = eos01)
tvt_match2 <- tvt_matching_num(data = tvtdata_num,
                               time_atrisk = time_atrisk,
                               time_eos = time_eos,
                               state_eos = state_eos,
                               state_treat = state_treat)
tvt_match2
```
